Regional Base-Flow Index in Arid Landscapes Using Machine Learning and Instrumented Records

### 2025-01-15 MANUSCRIPT.qmd
Update MANUSCRIPT.qmd

Directly measuring base flow and BFI presents unique challenges [@eckhardt2008]. The technique chosen to separate base flow has been shown to affect results, and the choice of base-flow separation method is subjective since ‘true’ BFI values are not known [@beck2013]. However, many methods have been developed to estimate these values. These methods include the use of tracers [@gonzales2009], graphical interpolation [@instituteofhydrology1980; @sloto1996], and digital filters [@arnold1995; @eckhardt2005; @lyne1979; @nathan1990]. These techniques have varying levels of applicability depending on the spatial scale, time span, and the scope of the study. Comparisons of various base-flow separation techniques have been made in previous studies [ e.g. @eckhardt2005; @eckhardt2008; @nathan1990]; this study does not explore the superiority of different methods.

@@

>>>>

Directly measuring base flow and BFI presents unique challenges [@eckhardt2008]. The technique chosen to separate base flow has been shown to affect results, and the choice of base-flow separation method is subjective since ‘true’ BFI values are not known [@beck2013]. However, many methods have been developed to estimate these values. These methods include the use of tracers [@gonzales2009], graphical interpolation [@instituteofhydrology1980; @sloto1996], and digital filters [@arnold1995; @eckhardt2005; @lyne1979; @nathan1990]. These techniques have varying levels of applicability depending on the spatial scale, time span, and the scope of the study. Comparisons of various base-flow separation techniques have been made in previous studies [e.g. @eckhardt2005; @eckhardt2008; @nathan1990]; this study does not explore the superiority of different methods.

@@

![Schematic of k-fold cross validation. The dataset is randomly divided into k stratified folds. Each fold serves as the validation set once, while the remaining folds are combined to create a training set for model development. Performance metrics for the test set are calculated and recorded, and this process is repeated for all k folds.](images/k-fold_fig.png){#fig-k-fold width="6000"}
